Supplemental Information A: Full Annotated Analysis and Reproducible Code

### 2022-05-05 Supplemental-Material-A-Annotated-Analysis.Rmd
sd plots added

# Mean Plots per Item

@@

```{r studentMeanViz, echo=FALSE, results='hide',fig.keep='all'} 
dtStudents$vizPlots <-
  lapply(seq_along(dtStudents$viz),
         function(i)
           meanVarPlot(dataIn = dtStudents$viz[[i]], 
                       name = names(dtStudents$viz)[[i]], 
                       namList = varNameListStudent))
dtStudents$vizPlots
```

@@

```{r medicalMeanViz, echo=FALSE, results='hide',fig.keep='all'} 
dtMedical$vizPlots <-
  lapply(seq_along(dtMedical$viz),
         function(i)
           meanVarPlot(dataIn = dtMedical$viz[[i]], 
                       name = names(dtMedical$viz)[[i]], 
                       namList = varNameListMedical))
dtMedical$vizPlots
```

@@

# **References**

>>>>

# **Plots per Item**

@@

### Mean Plots

```{r studentMeanViz, echo=FALSE, results='hide',fig.keep='all'} 
dtStudents$vizPlotsMean <-
  lapply(seq_along(dtStudents$viz),
         function(i)
           statVarPlot(dataIn = dtStudents$viz[[i]], 
                       name = names(dtStudents$viz)[[i]], 
                       namList = varNameListStudent,
                       stat = "mean")
         )
dtStudents$vizPlotsMean
```

### SD Plots

```{r studentSdViz, echo=FALSE, results='hide',fig.keep='all'} 
dtStudents$vizPlotsSd <-
  lapply(seq_along(dtStudents$viz),
         function(i)
           statVarPlot(dataIn = dtStudents$viz[[i]], 
                       name = names(dtStudents$viz)[[i]], 
                       namList = varNameListStudent,
                       stat = "sd")
         )
dtStudents$vizPlotsSd
```

@@

### Mean Plots

```{r medicalMeanViz, echo=FALSE, results='hide',fig.keep='all'} 
dtMedical$vizPlotsMean <-
  lapply(seq_along(dtMedical$viz),
         function(i)
           statVarPlot(dataIn = dtMedical$viz[[i]], 
                       name = names(dtMedical$viz)[[i]], 
                       namList = varNameListMedical,
                       stat = "mean")
         )
dtMedical$vizPlotsMean
```

### SD Plots

```{r medicalSdViz, echo=FALSE, results='hide',fig.keep='all'} 
dtMedical$vizPlotsSd <-
  lapply(seq_along(dtMedical$viz),
         function(i)
           statVarPlot(dataIn = dtMedical$viz[[i]], 
                       name = names(dtMedical$viz)[[i]], 
                       namList = varNameListMedical,
                       stat = "sd")
         )
dtMedical$vizPlotsSd
```

@@

<!-- # **References**   -->
